---
title: "Datachecks Tracking Task A, N = 12/23"
output:
  html_document:
    toc: TRUE
---
# preparations

1) install packages

```{r}
library(ggplot2) #plots
library(reticulate) # read npz files
```


2) define variables & paths
3) load data for all subjects, all trials in nested list

```{r load data, echo = T}
trials = 72

behav_dir = ("R:/AG-Beste-Studien/Emulation/04_data/behav")
behav_subdirs = grep(list.files(behav_dir, pattern = "*_A"), pattern = "csv|npz", invert = TRUE, value = TRUE)

list_all_sub = list()

for (i in 1: length(behav_subdirs)){
  subj_path = paste(behav_dir, "/", behav_subdirs[i], sep = "")
  setwd(subj_path)
  list_all_sub[[i]] = list()
  names(list_all_sub)[i] = behav_subdirs[i]
  for (j in 1: trials){
    name_trialfile = paste(strsplit(behav_subdirs[i], split = "_")[[1]][1], "_traj_purs_", j, ".csv", sep = "")
    list_all_sub[[i]][[j]] = read.csv(name_trialfile, header = T, sep = ",")
  }
}

```
# overview
## some basic plots

plots for trajectory, pursuit and error curve, single trial

```{r plots_single_trial, echo = T}
library(ggplot2)

df_038GC_20 = as.data.frame(list_all_sub$`038GC_A`[[70]])

ggplot(data = df_038GC_20, aes(x = (1:length(traj.x))/60, y = traj.y)) +
  #ggtitle("038GC_A, trial 1") +
  geom_line() +
  geom_line(aes(x = (1:length(traj.x))/60, y = purs.y), color= "blue")+
  geom_line(aes(x = (1:length(traj.x))/60, y = error), color = "red") +
  labs(x = "seconds", y = "")
  

```


## some statistics on mean error

1) load trialfiles for all subjects
2) save as list for further analyses

```{r}
trials = 72

behav_dir = ("R:/AG-Beste-Studien/Emulation/04_data/behav")
behav_subdirs = grep(list.files(behav_dir, pattern = "*_A"), pattern = "csv|npz", invert = TRUE, value = TRUE)

list_trial_info = list()

for (i in 1: length(behav_subdirs)){
  subj_path = paste(behav_dir, "/", behav_subdirs[i], sep = "")
  setwd(subj_path)
  list_trial_info[[i]] = list()
  names(list_trial_info)[i] = behav_subdirs[i]
  name_trialfile = paste(behav_subdirs[i], "_trialdata.csv", sep = "")
  list_trial_info[[i]] = read.csv(name_trialfile, header = T, sep = ",")
}

```

### mean error across trial

to check if the error peak at trial start is just noise 

```{r}
trials = 72

behav_dir = ("R:/AG-Beste-Studien/Emulation/04_data/behav")
markers_dir = ("R:/AG-Beste-Studien/Emulation/05_automagic/Analyzer/export")

behav_subdirs = grep(list.files(behav_dir, pattern = "*_A"), pattern = "Tracking|Traj", invert = TRUE, value = TRUE)
marker_files = list.files(markers_dir, pattern = "pp_AM.*_A_removed_practice_with_last_trigger.Markers")

# get subject ids from marker files (not all behavioral datasets have markerfiles)
subject_ids = vector()
for (i in 1:length(marker_files)) {
  subject_ids[i] = strsplit(marker_files[i], split = "_")[[1]][3]
}

means_all = matrix(NA, 72, 400)
for (i in 1: trials) {
  this_trial_means = matrix(NA, 12, 400)
  for (ii in 1:length(subject_ids)) {
    this_trial_means[ii, ] = as.data.frame(list_all_sub[[ii]][i])$error_abs[1:400]
  }
  means_all[i, ] = colMeans(this_trial_means)
}
means_time = colMeans(means_all)
plot(means_time, type = "l", ylab = "mean error across subjects", xlab = "frames")

```

systematic peak of error during the first 100 frames --> only analyze from 100th frame on 

### check RMSD for single subject

```{r}
df_09WM9 = as.data.frame(list_trial_info$`09WM9_A`)
ggplot(data = df_09WM9) +
  geom_line(aes(x = Trial, y = rmsd)) +
  geom_hline(aes(yintercept = median(rmsd)))

```

### check rmsd for all subjects

one dataframe with all trials for all subjects

```{r eval = F}
dataframe_all = matrix(nrow = trials, ncol = length(behav_subdirs))
for (i in 1: length(behav_subdirs)){
 dataframe_all[ ,i] = list_trial_info[[i]]$rmsd
}
colnames(dataframe_all) = behav_subdirs

dataframe_all = t(dataframe_all)
colnames(dataframe_all) = 1:72
```

### calculate mean over subjects, plot trials

```{r eval = F}
means_sub = rowMeans(dataframe_all)
plot(means_sub, type = "l")
```

### compare early and late trials
early trials: trial 20-30
late trials: trial 60-70
calculate mean for trialsets and save as dataframe

```{r eval = F}
t.test(dataframe_all[20:29, ], dataframe_all[60:69, ])

```
# compare constant and random trajectory performance

## prepare the data

Read trigger data and get behavioral frames for trigger 27, 23, 24, 12

then, calculate mean error for random and constant trajectory parts and compare

```{r, echo = T, eval = F}

behav_dir = ("R:/AG-Beste-Studien/Emulation/04_data/behav")
markers_dir = ("R:/AG-Beste-Studien/Emulation/05_automagic/Analyzer/export")

behav_subdirs = grep(list.files(behav_dir, pattern = "*_A"), pattern = "Tracking|Traj", invert = TRUE, value = TRUE)
marker_files = list.files(markers_dir, pattern = "pp_AM.*_A_removed_practice_with_last_trigger.Markers")

# get subject ids from marker files (not all behavioral datasets have markerfiles)
subject_ids = vector()
for (i in 1:length(marker_files)) {
  subject_ids[i] = strsplit(marker_files[i], split = "_")[[1]][3]
}
for (j in 1:length(subject_ids)) {
  this_subdir = paste(behav_dir, "/", subject_ids[j], "_A", sep= "")
  this_markerfile = marker_files[j]
  setwd(this_subdir)
  trialfiles = list.files(this_subdir, pattern = "*_traj_")
  setwd(markers_dir)
  trialsamples = vector()
  markerfile = as.data.frame(read.table(this_markerfile, skip = 1, sep = ",", header = T)[, 2:3])
  rows_markers = which(markerfile[1] == " S 27" | markerfile[1] == " S 23" | markerfile[1] == " S 24" | markerfile[1] == " S 12" | markerfile[1] == " S 16")
  trial_markers = markerfile[rows_markers, ]
  rownames(trial_markers) = NULL
  trial_markers[ ,3] = NA
  trial_markers[ ,4] = NA
  colnames(trial_markers) <- c("marker", "eeg_sample", "trial_sample", "perc")
  rows_27 = which(trial_markers[,1] == " S 27")
  for (k in 1: length(rows_27)) {
    trial_markers[rows_27[k] +1, 3] = trial_markers[rows_27[k] +1, 2] - trial_markers[rows_27[k], 2]
    trial_markers[rows_27[k] +2, 3] = trial_markers[rows_27[k] +2, 2] - trial_markers[rows_27[k], 2]
    trial_markers[rows_27[k] +3, 3] = trial_markers[rows_27[k] +3, 2] - trial_markers[rows_27[k], 2]
    trial_markers[rows_27[k], 3] = 0
  }
  trial_markers = trial_markers[complete.cases(trial_markers[ , 3]), ]
  rows_12_16 = which(trial_markers[,1] == " S 12"  | trial_markers[,1] == " S 16")
  rows_27 = which(trial_markers[,1] == " S 27")
  for (l in 1: length(rows_12_16)) {
    trial_markers[rows_12_16[l], 4] = trial_markers[rows_12_16[l], 3] / trial_markers[rows_12_16[l], 3]
    trial_markers[rows_12_16[l] -1, 4] = trial_markers[rows_12_16[l] -1, 3] / trial_markers[rows_12_16[l], 3]
    trial_markers[rows_12_16[l] -2, 4] = trial_markers[rows_12_16[l] -2, 3] / trial_markers[rows_12_16[l], 3]
    trial_markers[rows_12_16[l] -3, 4] = trial_markers[rows_12_16[l] -3, 3] / trial_markers[rows_12_16[l], 3]
  }
  setwd(this_subdir)
  for (z in 1: length(trialfiles)) {
    #list_all_reduced[[j]][[z]] = list()
    trial_df = read.csv(trialfiles[z], header = T, sep = ",")
    start_const = (ceiling(trial_markers[rows_27[z]+ 1, 4] * nrow(trial_df)))
    end_const = (ceiling(trial_markers[rows_27[z]+ 2, 4] * nrow(trial_df))) 
    rand1 = trial_df[1:start_const, ]
    rand2 = trial_df[end_const: nrow(trial_df), ]
    const = trial_df[start_const:end_const, ]
    file_const = paste(subject_ids[j], "_const_", z, ".csv", sep = "")
    file_rand1 = paste(subject_ids[j], "_rand1_", z, ".csv", sep = "")
    file_rand2 = paste(subject_ids[j], "_rand2_", z, ".csv", sep = "")
    write.csv(const, file = file_const)
    write.csv(rand1, file = file_rand1)
    write.csv(rand2, file = file_rand2)
  }
}


```

## create dataframe with all subjects and means

```{r create_df, eval = F, echo = T}
behav_dir = ("R:/AG-Beste-Studien/Emulation/04_data/behav")
markers_dir = ("R:/AG-Beste-Studien/Emulation/05_automagic/Analyzer/export")

behav_subdirs = grep(list.files(behav_dir, pattern = "*_A"), pattern = "Tracking|Traj", invert = TRUE, value = TRUE)
marker_files = list.files(markers_dir, pattern = "pp_AM.*_A_removed_practice_with_last_trigger.Markers")

# get subject ids from marker files (not all behavioral datasets have markerfiles)
subject_ids = vector()
for (i in 1:length(marker_files)) {
  subject_ids[i] = strsplit(marker_files[i], split = "_")[[1]][3]
}

trials = 72

dataframe = data.frame()
for (i in 1: length(subject_ids)) {
  this_subdir = paste(behav_dir, "/", subject_ids[i], "_A", sep= "")
  setwd(this_subdir)
  dataframe[i, 1] = subject_ids[i]
  const_data = vector()
  rand1_data = vector()
  rand2_data = vector()
  wholetrial_data = vector()
  
  for (ii in 1: trials) {
    filename = paste(subject_ids[i], "_const_", ii, ".csv", sep = "")
    data_const = read.csv(filename, header = T, sep = ",")
    const_data[ii] = mean(data_const$error_abs)
    
    filename = paste(subject_ids[i], "_rand1_", ii, ".csv", sep = "")
    data_rand1 = read.csv(filename, header = T, sep = ",")
    rand1_data[ii] = mean(data_rand1$error_abs)
    
    filename = paste(subject_ids[i], "_rand2_", ii, ".csv", sep = "")
    data_rand2 = read.csv(filename, header = T, sep = ",")
    rand2_data[ii] = mean(data_rand2$error_abs)
    
    filename = paste(subject_ids[i], "_traj_purs_", ii, ".csv", sep = "")
    data_wt = read.csv(filename, header = T, sep = ",")
    wholetrial_data[ii] = mean(data_wt$error_abs)
    
  }
  dataframe[i, 2] = mean(const_data)
  dataframe[i, 3] = mean(rand1_data)
  dataframe[i, 4] = mean(rand2_data)
  dataframe[i, 5] = mean(wholetrial_data)
}
colnames(dataframe) = c("subject_id", "mean_const", "mean_rand1", "mean_rand2", "mean_whole_trial")

setwd(behav_dir)
write.csv(dataframe, file = "20210903_dataframe_means.csv")

```

## create dataframe with all subjects and means, split for early and late trials

```{r, eval = F}

behav_dir = ("R:/AG-Beste-Studien/Emulation/04_data/behav")
markers_dir = ("R:/AG-Beste-Studien/Emulation/05_automagic/Analyzer/export")

behav_subdirs = grep(list.files(behav_dir, pattern = "*_A"), pattern = "Tracking|Traj", invert = TRUE, value = TRUE)
marker_files = list.files(markers_dir, pattern = "pp_AM.*_A_removed_practice_with_last_trigger.Markers")

# get subject ids from marker files (not all behavioral datasets have markerfiles)
subject_ids = vector()
for (i in 1:length(marker_files)) {
  subject_ids[i] = strsplit(marker_files[i], split = "_")[[1]][3]
}

trials = 72

list_subjects = list()
for (i in 1: length(subject_ids)) {
  this_subdir = paste(behav_dir, "/", subject_ids[i], "_A", sep= "")
  setwd(this_subdir)
  dataframe[i, 1] = subject_ids[i]
  const_data = vector()
  rand1_data = vector()
  rand2_data = vector()
  wholetrial_data = vector()
  list_subjects[[i]] = list()
  
  for (ii in 1: trials) {
    filename = paste(subject_ids[i], "_const_", ii, ".csv", sep = "")
    data_const = read.csv(filename, header = T, sep = ",")
    const_data[ii] = mean(data_const$error_abs)
    
    filename = paste(subject_ids[i], "_rand1_", ii, ".csv", sep = "")
    data_rand1 = read.csv(filename, header = T, sep = ",")
    rand1_data[ii] = mean(data_rand1$error_abs)
    
    filename = paste(subject_ids[i], "_rand2_", ii, ".csv", sep = "")
    data_rand2 = read.csv(filename, header = T, sep = ",")
    rand2_data[ii] = mean(data_rand2$error_abs)
    
    filename = paste(subject_ids[i], "_traj_purs_", ii, ".csv", sep = "")
    data_wt = read.csv(filename, header = T, sep = ",")
    wholetrial_data[ii] = mean(data_wt$error_abs)
    
  }
  
  list_subjects[[i]]$const = const_data
  list_subjects[[i]]$rand1 = rand1_data
  list_subjects[[i]]$rand2 = rand2_data
  list_subjects[[i]]$wholetrial = wholetrial_data
}

# prepare dataframe

dataframe = data.frame()
for (i in 1: length(subject_ids)) {
  dataframe[i, 1] = subject_ids[i]
  dataframe[i, 2] = mean(list_subjects[[i]]$wholetrial[1:24])
  dataframe[i, 3] = mean(list_subjects[[i]]$wholetrial[25:48])
  dataframe[i, 4] = mean(list_subjects[[i]]$wholetrial[49:72])
  dataframe[i, 5] = mean(list_subjects[[i]]$const[1:24])
  dataframe[i, 6] = mean(list_subjects[[i]]$const[25:48])
  dataframe[i, 7] = mean(list_subjects[[i]]$const[49:72])
  dataframe[i, 8] = mean(list_subjects[[i]]$rand1[1:24])
  dataframe[i, 9] = mean(list_subjects[[i]]$rand1[25:48])
  dataframe[i, 10] = mean(list_subjects[[i]]$rand1[49:72])
  dataframe[i, 11] = mean(list_subjects[[i]]$rand2[1:24])
  dataframe[i, 12] = mean(list_subjects[[i]]$rand2[25:48])
  dataframe[i, 13] = mean(list_subjects[[i]]$rand2[49:72])
}
colnames(dataframe) = c("subject", "wholetrial1", "wholetrial2", "wholetrial3", "const1", "const2", "const3", "rand11", "rand12", "rand13", "rand21", "rand22", "rand23")

setwd("R:/AG-Beste-Studien/Emulation/04_data")
write.csv(dataframe, file = "behav_means.csv")

```

# exploratory analysis task C

read data

1) trialdata C --> velocity, accuracy

```{r eval = F, echo=T}

#set data directory
# datadir = ("R:/AG-Beste-Studien/Emulation/04_data/behav/00_npz_files")
datadir = ("/Users/adriana/Dropbox/transfer_kjp/210909_behav_data")
setwd(datadir)

#packages
library(reticulate)

#import python 
np <- import("numpy")

#read files + number of subjects

n_files_C = length(list.files(datadir, pattern = "Tracking.*_C"))
files_C =  list.files(datadir, pattern = "Tracking.*_C")

#subject ids
sbj_ids = vector()
for (i in 1:n_files_C) {
  sbj_ids[i] = strsplit(files_C[i], split = "-")[[1]][2]
  sbj_ids[i] = strsplit(sbj_ids[i], split = "_")[[1]][1]
}

trialnum = 72

#load data from npz, save as list

list_c = list()
for (i in 1:n_files_C) {
  filename = paste("Tracking-", sbj_ids[i], "_C-Trials.npz", sep = "")
  data <- np$load(filename, allow_pickle = TRUE)
  data_list = data$f[["arr_0"]][[1]]
  list_c[[i]] = data_list
}

names(list_c) <- sbj_ids

rm(data_list)
rm(filename)

#create dataframe for every subject

# output_dir = ("R:/AG-Beste-Studien/Emulation/04_data/behav")
output_dir = ("/Users/adriana/Dropbox/transfer_kjp")
setwd(output_dir)

for (i in 1:length(sbj_ids)) {
  df = as.data.frame(cbind(as.vector(unlist(list_c[[i]]$Velocity)), list_c[[i]]$Direction, list_c[[i]]$Accuracy_C))
  colnames(df) <- c("vel", "dir", "accuracy")
  filename = paste(sbj_ids[i], "_trials_c.csv", sep = "")
  write.csv(df, file = filename, row.names = T)
}

```

2) trajectory choice

```{r eval = F, echo = T}

#set data directory
datadir = ("R:/AG-Beste-Studien/Emulation/04_data/behav/00_npz_files")
setwd(datadir)

#packages
library(reticulate)

#import python 
np <- import("numpy")

#read files + number of subjects

choice_files =  list.files(datadir, pattern = "Traj_choice*")

#subject ids
sbj_ids = vector()
for (i in 1:length(choice_files)) {
  sbj_ids[i] = strsplit(choice_files[i], split = "-")[[1]][2]
  sbj_ids[i] = strsplit(sbj_ids[i], split = "_")[[1]][1]
}

# extract data from npz file

list_traj_choice = list()

for (i in 1:length(sbj_ids)) {
  filename = paste("Traj_choice-", sbj_ids[i], "_C.npz", sep = "")
  data <- np$load(filename, allow_pickle = TRUE)
  data_list = data$f[["arr_0"]][[1]]
  list_traj_choice[[i]] = data_list
}


```


